%% The MIT License (MIT)
%%
%% Original work Copyright (c) 2015 Daniil Belyakov
%% Modified work Copyright (c) 2017 Paul Olteanu
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.
\documentclass[calibri]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Paul Olteanu}
\address{26 Willowbrook Rd \linebreak Thornhill, ON}
\contacts{(647) 449-6597 \linebreak p.a.olteanu@gmail.com}

\begin{document}

    % Print the header
    \makeheader

    % Print the content
    \begin{cvsection}{\Large{Summary of Skills}}
        \begin{cvsubsection}{Languages + Frameworks}{}{}
            \begin{itemize}
                \item Elixir | Python + Flask | C | Ruby + Rails | C++ | SQL | HTML | CSS | Javascript
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Technologies}{}{}
            \begin{itemize}
                \item Linux | AWS EC2 | Docker | Postgres | MongoDB | Arduino | DipTrace
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    \begin{cvsection}{\Large{Employment}}
        \begin{cvsubsection}{Full Stack Developer}{Hashtag Paid}{January 2018 -- April 2018}
            Post \& User data collector
            \begin{itemize}
                \item Created project spec with CTO detailing project scope and user story
                \item Architected genstage pipeline with worker backpressure \& rate limiting to parallelize data collection jobs
                \item Created adapters for interfacing with Twitter \& Youtube APIs, and web-scraping Instagram data
                \item Using engagement rate and follower data, created post querying timeline to maximize collected engagements
                \item Set up squid proxy servers to spread requests across IPs
                \item Languages and technologies: \textbf{Elixir + GenStage}, \textbf{AWS}, \textbf{MongoDB}, \textbf{Docker}, \textbf{Squid}
            \end{itemize}

            RFP wizard
            \begin{itemize}
                \item Led project creating multi-step form used by companies to request a campaign proposal
                \item Updated old-style campaign model to collet more data for accounts team
                \item Worked closely with UI/UX designer, creating mockup of online campaign proposal tool
                \item Languages and technologies: \textbf{Ruby + Rails}, \textbf{AWS}, \textbf{Postgres}, \textbf{HTML}, \textbf{CSS}, \textbf{Javascript}
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    \begin{cvsection}{\Large{Projects}}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf{Hardware Logic Gate Simulator (2017):} Logic gate simulator (AND, OR, XOR, NAND), for the Onion Omega 2 embedded system. Config done through CSV file. \textbf{C}
                \item \textbf{Custom Version Control System (2017):} VCS loosely modeled after git. Supports commit messages, reverting, and a full history view. Represents commits through file diffs instead of full copies to reduce storage footprint. \textbf{Python + Click}
                \item \textbf{CHIP-8 emulator (2016):} An emulator for the 35 opcode CHIP-8 interpreted language. \textbf{C + SDL}
                \item \textbf{Image sharing website (2016):} Image sharing website similar to Reddit and Instagram. Allows for multiple sorting algorithms and uses DB-side pagination. \textbf{Python + Flask}, \textbf{AWS}, \textbf{Heroku}, \textbf{Postgres}
                \item \textbf{Memory allocator (2016):} Reimplementation of \code{malloc} and \code{free} within a 16MB memory block. Uses the boundary-tag method to keep track of allocated and free memory. \textbf{C}
                \item \textbf{Tuple library (2015):} Implementation of the \code{Keyword} API for binary types. Published on Hex (the Elixir/ Erlang package manager), with 600 installs. \textbf{Elixir}
            \end{itemize}
            Source code and other projects at \underline{github.com/PaulOlteanu}
        \end{cvsubsection}
    \end{cvsection}

    \begin{cvsection}{\Large{Additional Experience and Awards}}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf{Leader of Computer Club (2015 -- 2017):} Held weekly meetings, helped students with projects, taught Python
                \item \textbf{President's scholarship (2017):} Awarded to students with admission averages between 90\% -- 94.9\%
                \item \textbf{Engineering entrance scholarship (2017):} Awarded to students with ``outstanding high school records and involvement in extracurricular activities''
                \item \textbf{Certificate of distinction, Canadian Computing Competition (2015 -- 2017):} Top 25\% of ~5000 participants
                \item \textbf{Certificate of distinction, Euclid Math Contest (2017):} Top 25\% of ~21000 participants
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

\end{document}
